---
title: "Assessing the impact of nonverbal communication cues in online teaching"
author: "Maria Osipenko, Kathrin Heller"
date: ""
output: 
 bookdown::pdf_document2:
    toc: false
    fig_caption: yes
    keep_tex: true
bibliography: [references.bib] 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

## Research question

Do different usage patterns of nonverbal communication cues of course instructor as colors, markers, paintings have impact on learning success in online format? 

For previous research see @ng2021, @dixson2016, @cheng2014, and @tawil2019.

## Retrospective feature extraction

We extract features retrospectively from lecture notes of three semesters and two courses on statistics.

```{r, echo=F}
#install.packages("Rpoppler")
#install.packages("magick")
files<-"/media/osipenko/maxone/Lehre/Statistik_2/Notizen/WS2020/Lektion1_1_Notizen.pdf"
content<-Rpoppler::PDF_text(files)
asimage<-magick::image_read_pdf(files)

```

```{r figPage, echo=FALSE, out.width='25%', fig.align='center', fig.cap='An example of lecture notes'}
asimage[1]
```

```{r, echo=F, include=F}
#extraction of text from the first page
itext<-magick::image_read(asimage[[1]])
text<-magick::image_ocr(itext,language="deu")#sudo apt-get install tesseract-ocr-deu
print(paste(substr(text[1],1,200),"..."))
#magick::image_ocr_data(itext,language="deu")
```

## Documentation of the data aquisition process


# Results

A table:

see our results in Table \@ref(tab:table00)

```{r table00,echo=FALSE}
library(knitr)
library(kableExtra)
options(scipen=999)
text_decr<-data.frame(Year=c(seq(2015,2019),"All years"), News=c("4,395","5,391","5,738","8,465","6,435","30,424"),
                      Words=c("823","840","923","1,352","1,401","1,114"))
 knitr::kable(text_decr, align = "llll",
               col.names = c("Year","News Articles (merged)","Average Word Count"),
               row.names = FALSE,
               #table.attr = "id=\"table1\"",
               digits = 0,
               caption = "Description of the final textual corpus"
  )
```



# Literature {-}

<div id="refs"></div>
